=== Run information ===

Scheme:       weka.classifiers.trees.J48 -C 0.25 -M 2
Relation:     Book1
Instances:    149
Attributes:   22
              Gender
              Age
              Marital Status
              Education
              Employment
              All the tasks you have performed, are taking much more time than usual.
              You are facing a lack of concentration.
              You are feeling you have no future.
              You are facing problems with making decisions
              You feel, your life is sad, as there is no joy in your life anymore.
              You have lost interest in all things that were important to you once upon a time.
              You have been feeling guilty for everything you do.
              You have been very irritated and angry recently
              You have been feeling very fatigued
              You are feeling that everything you have done has been a failure
              You are having a lack of sleep
              You are having suicidal thoughts
              You have lost or gained weight without any diet programs.
              You are having a loss of appetite.
              You are having trust issues with everyone around you.
              You are having trouble in all your relationships (home as well as professional)
              Depression
Test mode:    evaluate on training data

=== Classifier model (full training set) ===

J48 pruned tree
------------------

You have been very irritated and angry recently <= 3
|   You are having trouble in all your relationships (home as well as professional) <= 3
|   |   You are facing problems with making decisions <= 3: YES (81.0/2.0)
|   |   You are facing problems with making decisions > 3
|   |   |   All the tasks you have performed, are taking much more time than usual. <= 2: YES (3.0)
|   |   |   All the tasks you have performed, are taking much more time than usual. > 2: NO (5.0)
|   You are having trouble in all your relationships (home as well as professional) > 3
|   |   You have been very irritated and angry recently <= 1: YES (2.0)
|   |   You have been very irritated and angry recently > 1
|   |   |   Gender = Female: NO (12.0)
|   |   |   Gender = Male
|   |   |   |   You have lost or gained weight without any diet programs. <= 2: YES (2.0)
|   |   |   |   You have lost or gained weight without any diet programs. > 2: NO (3.0)
You have been very irritated and angry recently > 3
|   You are having a lack of sleep <= 1
|   |   You are feeling you have no future. <= 4: YES (2.0)
|   |   You are feeling you have no future. > 4: NO (3.0)
|   You are having a lack of sleep > 1: NO (36.0)

Number of Leaves  : 	10

Size of the tree : 	19


Time taken to build model: 0.01 seconds

=== Evaluation on training set ===

Time taken to test model on training data: 0 seconds

=== Summary ===

Correctly Classified Instances         147               98.6577 %
Incorrectly Classified Instances         2                1.3423 %
Kappa statistic                          0.9721
Mean absolute error                      0.0262
Root mean squared error                  0.1144
Relative absolute error                  5.4119 %
Root relative squared error             23.2687 %
Total Number of Instances              149     

=== Detailed Accuracy By Class ===

                 TP Rate  FP Rate  Precision  Recall   F-Measure  MCC      ROC Area  PRC Area  Class
                 1.000    0.033    0.978      1.000    0.989      0.972    0.985     0.980     YES
                 0.967    0.000    1.000      0.967    0.983      0.972    0.985     0.981     NO
Weighted Avg.    0.987    0.019    0.987      0.987    0.987      0.972    0.985     0.981     

=== Confusion Matrix ===

  a  b   <-- classified as
 88  0 |  a = YES
  2 59 |  b = NO

